---
title: "EDAV Project 1"
output: html_document
---

```{r}
#############################
# < Waitlist Survivors >
#
# STAT W4701 
# Homework < 01 >
# < Feb 11th >
#
#############################
#setwd("~/Documents/Study/Spring 2016/EDAV")

library(xlsx)
library(reshape)


# Read xlsx file
raw.data <- read.xlsx("../docs/Survey_Response.xlsx", sheetName = "Form Responses 1")
data <- raw.data


# drop empty columns
data <- data[, colSums(is.na(data)) < nrow(data)]


# Clean up variable names
cleaned.names <- c('waitlist', 'program','tools','exp.R.manipulation',
          'gender','text.editor','exp.R.graphics','exp.R.advanced','exp.R.reproducible','exp.Matlab','exp.Github')
names(data) <- cleaned.names

library(stringr)
# Split tools column into multiple columns
## Count the maximum number of commas per row in the tools column
num.commas <- max(sapply(gregexpr(",", data$tools, fixed = TRUE), function(x) max(length(x)))) + 1
## Split the tools column in separate columns
tool.cols <- colsplit(data$tools,"[,]",names=sapply(1:num.commas, function(x) paste('tools', x, sep='')))
tool.cols <- sapply(tool.cols, str_trim)
unique.tool.values <- unique(unlist(lapply(tool.cols, FUN=unique)))

tool.matrix <- matrix(0, nrow = nrow(tool.cols),20)

tool.names <- unique.tool.values
colnames(tool.matrix) <- tool.names
tool.matrix <- as.data.frame(tool.matrix)
for (i in 1:ncol(tool.cols) ) {
      for (tool.name in tool.names) {
          tool.matrix[which(tool.cols[, i] == tool.name), tool.name] <- 1
          }
}

clean.tool.names <- c("R", "Excel", "Matlab", "RStudio", "Github", "SQL", "Shell", "Python", "SPSS", "ggplot2", "GDrive", "Web", "C", "Dropbox", "Regex", "Stata", "LaTeX", "Sweave", "XML", "Lattice")
names(tool.matrix) <- clean.tool.names
data <- cbind(data, tool.matrix)
data <- subset(data, select=-c(tools))


# Clean up inconsistent program values
levels(data$program)
sort(table(data$program))
levels(data$program)[levels(data$program)=="Ms in ds"] <- "IDSE (master)"
levels(data$program)[levels(data$program)=="MSDS"] <- "IDSE (master)"
levels(data$program)[levels(data$program)=="PhD Biomedical Informatics"] <- "Ph.D."
levels(data$program)[levels(data$program)=="Data Science"] <- "Unknown"


# Clean up text editor values
levels(data$text.editor)
sort(table(data$text.editor))
# Remove extra spaces
data$text.editor <- factor(str_trim(data$text.editor))

levels(data$text.editor)[levels(data$text.editor)=="textwrangler"] <- "TextWrangler"
levels(data$text.editor)[levels(data$text.editor)=="Text Wrangler"] <- "TextWrangler"
levels(data$text.editor)[levels(data$text.editor)=="textWrangler"] <- "TextWrangler"

levels(data$text.editor)[levels(data$text.editor)=="Sublime"] <- "Sublime Text"
levels(data$text.editor)[levels(data$text.editor)=="Sublime Text 2"] <- "Sublime Text"
levels(data$text.editor)[levels(data$text.editor)=="sublime"] <- "Sublime Text"
levels(data$text.editor)[levels(data$text.editor)=="Sublime Text!"] <- "Sublime Text"
levels(data$text.editor)[levels(data$text.editor)=="sublime text 2"] <- "Sublime Text"
levels(data$text.editor)[levels(data$text.editor)=="Sublime 2"] <- "Sublime Text"
levels(data$text.editor)[levels(data$text.editor)=="sublime text"] <- "Sublime Text"

levels(data$text.editor)[levels(data$text.editor)=="I used jupyter last semester"] <- "Jupyter"
# Ipython is now known as Jupyter
levels(data$text.editor)[levels(data$text.editor)=="Ipython"] <- "Jupyter"

levels(data$text.editor)[levels(data$text.editor)=="haven't used any"] <- "None"






# Assign level ordering to experience variables
experience.cols <- names(data)[grepl("^exp.", names(data))]
for (exp.col in experience.cols) {
  data[, exp.col] <- factor(data[, exp.col], levels=levels(data[, exp.col])[c(4, 1, 2, 3)], ordered=TRUE)
}

barplot(table(data$waitlist))
barplot(table(data$exp.R.manipulation))
barplot(table(data$exp.R.advanced, data$program))


barplot(sort(sapply(data[11:30], sum), decreasing=FALSE), horiz=TRUE)

# Correlation plot
library(ellipse)
ctab <- cor(data[, 11:30])
distance <- as.dist(1 - ctab)
# http://datascienceplus.com/hierarchical-clustering-in-r/
plot(hclust(distance), 
     main="Dissimilarity = 1 - Correlation", xlab="")
ordering <- hclust(distance)$labels[hclust(distance)$order]

round(ctab, 2)
colorfun <- colorRamp(c("#CC0000","white","#3366CC"), space="Lab")
plotcorr(ctab[ordering,ordering], col=rgb(colorfun((ctab[ordering,ordering]+1)/2), maxColorValue=255),
         mar = c(0.1, 0.1, 0.1, 0.1))

```

```{r results="asis" }
#install.packages("rjson")
#install.packages("rCharts")
#install.packages("devtools")
#install.packages("Rcpp")
#install_github('ramnathv/rCharts')


library(devtools)
library(Rcpp)
require('httr')
require(rCharts)
require(rjson)

p5 <- rCharts$new()
p5 <- nPlot(~program, data = data, type = 'pieChart')
p5$chart(donut = TRUE)
p5$print('iframe',  include_assets=TRUE)

#Sankey Graph
data_t=as.data.frame(table(data$program,data$text.editor))
#remove all data with 0 relations
data_t=data_t[data_t[,3]>0,]
colnames(data_t) <- c("source", "target", "value")
sankeyPlot <- rCharts$new()
sankeyPlot$setTemplate(script = "./rCharts_d3_sankey-gh-pages/layouts/chart.html")
sankeyPlot$setLib('http://timelyportfolio.github.io/rCharts_d3_sankey/libraries/widgets/d3_sankey')
sankeyPlot$set(
  data = data_t,
  nodeWidth = 15,
  nodePadding = 10,
  layout = 32,
  width = 800,
  height = 500,
  units = "TWh",
  title = "Editor-Program"
)
#sankeyPlot$publish("Sankey by Tool")
save_stdout <- function(x){
  paste(capture.output(x), collapse = '\n')
}
#save_stdout(sankeyPlot$show('inline', include_assets = TRUE, standalone = TRUE))
sankeyPlot$print('iframesrc',  include_assets=TRUE)

```

``````{r results="asis" }



col.names.data=c("exp.R.advanced","exp.Github","exp.R.reproducible"
                 ,"exp.R.manipulation","exp.R.graphics","exp.Matlab")
matrix={}
for (name.col in col.names.data){
  row=cbind(name.col,data[,name.col])
  matrix=rbind(matrix,row)
}
data.boxplot=as.data.frame(matrix)
colnames(data.boxplot)=c("tool","experience")

n2<-rCharts$new()
n2 = nPlot( ~experience,group="tool", data = data.boxplot, type = "multiBarChart")
n2$print('inline',  include_assets=TRUE)
```